Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2021-03-30 02_Paper/paper.tex
corresponding author
fix link.

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Heinbach}
\author[a]{Fabian Steinberg*} 
\author[a]{Alejandro R. Pérez M.}
\author[a]{Lennart Schmallenbach}
\author[b,c,d]{Jochen Garcke}
\author[b]{Daniela Steffes-lai}
\author[b,c,e]{Moritz Wolter}

@@

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}

@@

We compared a total of three different classifier architectures on the data,
a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work well.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

>>>>

\author[a]{Peter Burggräf}
\author[a]{Johannes Wagner}
\author[a]{Benjamin Heinbach}
\author[a]{Fabian Steinberg} 
\author[a]{Alejandro R. Pérez M.*}
\author[a]{Lennart Schmallenbach}
\author[b,c,d]{Jochen Garcke}
\author[b]{Daniela Steffes-lai}
\author[b,c,e]{Moritz Wolter}

@@

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} alejandro.perez@uni-siegen.de}

@@

We compared a total of three different classifier architectures on the data,
a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work well.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/USi-IPEM/Demo-Cell-Classification}}
